### 2023-12-17 slides/slides.tex
.

\documentclass[10pt]{beamer}

\usepackage{amsfonts}
\usepackage{subfiles}
\usepackage[T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[russian]{babel}

\usepackage{amsmath, amsfonts, amssymb, amsthm, mathtools, mathrsfs}
\usepackage{wasysym, dsfont}
\usepackage{graphicx}
\usepackage{float}
\usepackage{wrapfig}

\usepackage{caption}
\usepackage{subcaption}
\usepackage{longtable}
% \usepackage{subfigure}

\usepackage{multicol}
\DeclareMathOperator*{\argmax}{\arg\!\max}
\DeclareMathOperator*{\argmin}{\arg\!\min}

\mode<presentation>
{
	\usetheme{boxes}
	\beamertemplatenavigationsymbolsempty

	\setbeamertemplate{footline}[page number]
	\setbeamersize{text margin left=1.5em, text margin right=2.0em}
}
\newcommand\blfootnote[1]{%
	\begingroup
	\renewcommand\thefootnote{}\footnote{#1}%
	\addtocounter{footnote}{-1}%
	\endgroup
}
\newcommand\FontUP{\fontsize{12}{12}\selectfont}

\title[]{Обучение взаимосвязанных информативных представлений в задаче генерации образов}
\author{Охотников Никита Владимирович}
\institute{МФТИ}
\date{2023-2024}

\begin{document}

{
\begin{frame}
  \titlepage
\end{frame}
}

\end{document}